---
title: "Labor Force Statistics Dataset"
output: html_document
---
```{r include = FALSE} 
source("scripts/education.R")
source("scripts/gender.R")
source("scripts/race.R")
source("scripts/summary.R")
source("scripts/table_summary.R")

```
This is our report the Labor Force Statistics Dataset from the [U.S. Bureau of Labor Statistics](https://data.bls.gov/cgi-bin/surveymost?ln). 

Below is a table displaying the pertinent observations we found. ......

```{r echo = FALSE}
# Put the variable name for your chart below this line. (the file is sourced, so just having the variable will display the chart.)

```

Below is a chart intended to show the relationship between Education and Unemployment Rate: 

```{r echo = FALSE}
# Put the variable name for your chart below this line. (the file is sourced, so just having the variable will display the chart.)

```



Below is a chart intended to show the relationship between Gender and Unemployment Rate: 
```{r echo = FALSE}
# Put the variable name for your chart below this line 

```



Below is a chart intended to show the relationship between Race and Unemployment Rate: 

```{r echo = FALSE}
# Put the variable name for your chart below this line 

```
